Paper \#ZW10157

### 2019-01-31 paper/submission/ZW10157-response-1.tex
adding text about new abstract

~\cite{hofler13,bazarov05,yrss:09,jefferson,gull1,gull2} \documentclass{article}
\usepackage{latexsym}
\usepackage{color}
\setlength{\parskip}{3mm}
\setlength{\parindent}{0pt}
\usepackage[margin=1in]{geometry}

@@

{\bf Our response:} {\color{blue} 
	To address this concern, the following was added on lines 28-41 in the updated manuscript:

@@

{\bf Our Response:} {\color{blue} This optimization was used for design of 
an experiment. There is not an alternative base line, i.e. this is the 
``first such solution for the AWA''. The points have not been operationally measured yet.
The following line was added to the abstract to address this:

``Optimized solutions found by the framework were used to finish the design 
of a two beam acceleration experiment.''
}

>>>>

\documentclass{article}
\usepackage{latexsym}
\usepackage{color}
\setlength{\parskip}{3mm}
\setlength{\parindent}{0pt}
\usepackage[margin=1in]{geometry}

@@

{\bf Our response:} {\color{blue} 
	Several changes were made in the paper to address this concern. 
	 abstract to explain the AWA problem. 
	Here is the new abstract in it's entirety:

	Particle accelerators are invaluable tools for research in the basic and applied sciences, such as materials science, chemistry,
	the biosciences, particle physics, nuclear physics and medicine. The design, commissioning, and operation of accelerator facilities is a
	non-trivial task, due to the large number of control parameters and the complex interplay of several conflicting design goals.
	The Argonne Wakefield Accelerator facility has some unique challenges resulting from its purpose to carry out advanced accelerator R\&D.
	Individual experiments often have challenging beam requirements, and the physical configuration of the beamlines is often changed
	to accommodate the variety of supported experiments. The need for rapid deployment of different operational settings
	further complicates the optimization work that must be done for multiple constraints and challenging operational regimes. 
	One example of this is an independently staged two-beam acceleration experiment which requires the construction 
	of an additional beamline (this is now in progress).  The high charge drive beam, well into the space charge regime, must be threaded
	through small aperture (17.6mm) decelerating structures.  
	In addition, the bunch length must be sufficiently short to maximize power generation in the decelerator.  
	We propose to tackle this problem by means of multi-objective optimization algorithms which also facilitate a parallel deployment.
	In order to compute solutions in a meaningful time frame, a fast and scalable software framework is required.
	In this paper, we present a general-purpose framework for simulation-based
	multi-objective optimization methods that allows the automatic investigation of optimal sets of machine parameters.
	Using evolutionary algorithms as the optimizer and \textsc{OPAL} as the forward solver, validation experiments and 
	results of multi-objective optimization problems in the domain of beam dynamics are presented. 
	Optimized solutions for the new high charge drive beamline found by the framework were used to finish the design 
	of a two beam acceleration experiment.
	The selected solution along with the associated beam parameters is presented.

	The following was added on lines 28-41 in the updated manuscript:

@@

{\bf Our Response:} {\color{blue} This optimization was used for design of 
an experiment. There is not an alternative base line, i.e. this is the 
``first such solution for the AWA''. The points have not been operationally measured yet.
Several sentences were added to the abstract to explain this. 
Please see new abstract used in response to Referee A, or updated manuscript.
}
